timesliced_random_cell_selection

### 2018-10-29 src/timesliced_random_cell_selection.Rmd
loop complete, started cell selection randomisation

ok so now I have a base list to work off... I have split the cells with presence data into a list by time-slice (split_obs_cell_yymm) (code in biological_data_prep)

```{r}
test_timeslice <- split_obs_cell_yymm[1]
test_timeslice <- as.data.frame(test_timeslice)
test_time_cell <- unique_cell_centroid
test_time_cell <- test_time_cell[!test_time_cell$cell_id %in% test_timeslice$X1998.10.cell_id, , drop = FALSE]
```
ok that works... but you need to pop into a loop and dynamically name the output (and create a .csv maybe)

```{r}

```

>>>>

ok so now I have a base list to work off...

Split the data_aea into timeslices (year/month).
All you need is the year, month, cell_id
```{r}
cell_yymm <- subset(data_aea, select= c(cell_id, year, month)) #create a new df with just cell_id, yr, month
split_cell_yymm <- split(cell_yymm, list(cell_yymm$year, cell_yymm$month), drop = TRUE)
```

What I want to do is for each time slice, create a list of all cells, then remove the ones where observations occured
ly name the output (and create a .csv with the name of the level being worked on)

Here is a loop to create a copy of the unique_cell_centroid dataframe, and give it the same name as the splitobs_cell_yymm level
.csv naming code courtesy of [nadizan/stack exchange](https://stackoverflow.com/questions/53045158/r-naming-csv-with-a-list-level-name-in-a-loop?noredirect=1#comment92990285_53045158)

Note that the file are saved in /src. Manually move them to output/bio/background

```{r}
no_timeslices <- length(split_cell_yymm) # how many levels (time slices) are in the list
for (i in 1:no_timeslices){
  timeslice <- split_cell_yymm[[i]]
  timeslice <- as.data.frame(test_timeslice)
  time_cell <- unique_cell_centroid
  time_cell <- test_time_cell[!test_time_cell$cell_id %in% test_timeslice$cell_id, , drop = FALSE]
  write.csv(test_time_cell, paste0(names(lapply(split_cell_yymm, names))[i], ".csv"), row.names = FALSE) 
}
```

Ok so now I have a bunch of .csv files containing cells where no observations occurred for a given timeslice.
Next step is to randomly select cells in each timeslice. Make sure you generate new files for each...

load the .csvs... [code](https://www.reed.edu/data-at-reed/software/R/reading_and_writing.html)

```{r}
bckrnd_folder <- "../output/bio/background/"      # path to folder that holds multiple .csv files
bckrnd_list <- list.files(path = bckrnd_folder, pattern="*.csv") # create list of all .csv files in folder

# read in each .csv file in file_list and create a data frame with the same name as the .csv file
for (i in 1:length(bckrnd_list)){
  assign(bckrnd_list[i], 
  read.csv(paste(bckrnd_folder, bckrnd_list[i], sep=''))
  )
  #now do something....

  }

```
and that something you are going to do is randomly select rows....
